### 2016-04-13 code/rmarkdown/supporting_information.Rmd
+ restructure folders + include pcadapt for outlier loci analysis

# define ggplot2 color wheel function
gg_color_hue <- function(n) {
	hues <- seq(15, 375, length=n+1)
	hcl(h=hues, l=65, c=100)[1:n]
}

pretty.paste <- function(x) {
	if (length(x)==1)
		return(x)
	x <- sort(x)
	x1 <- paste(x[-length(x)], collapse',')
	x1 <- paste0(x1, ' and ', x[length(x)])
	return(x1)
}
```

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap=paste0('Species distributions. Squares represent planning units. For a given species, planning units that were found to be inhabited are denoted with bright blue. Note that \\textit{',pretty.paste(gsub('\\_', '\\ ', missing.species)),'} were omitted from analysis.')}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
		z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
		names(z)[4] <- 'presence'
		z$species <- gsub('\\_', ' ', x)
		return(z)
	}
)
# plot species data
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spp.grid.FPLY, aes(x=long, y=lat, 
		group=group, fill=presence), alpha=0.8, color='grey10') +
	theme_classic() +
	guides(fill=guide_legend(title='Presence')) +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', face='italic'),
		axis.title=element_blank()
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) +
	facet_wrap(~ species, ncol=4)
```

```{r, echo=FALSE, fig.width=4, fig.height=2.5, fig.cap="Species richness. Squares denote planning units. Planning units with a darker color are inhabited by more species."}
# calculate species richness
grid.PLY$Species_richness <- grid.PLY@data %>%
	select(5:(4+n_distinct(spp.samples.DF$species))) %>% as.matrix() %>% rowSums()
# plot species richness
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat, 
		group=group, fill=Species_richness), color='grey10') +
	scale_fill_gradientn(name='Richness (#)',
		colors=brewer.pal(9,'PuBu'),
		guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
	) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
		panel.border=element_rect(color='black', fill=NA, size=1)
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	)
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=10, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Each line denotes a different model parametrization. Asterisks indicate the model and number of populations with the most support.'}
# format data
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		curr.MTX <- spp.Mclust.LST[[i]]$mclust$BIC
		attr(curr.MTX, 'dim') <- c(nrow(curr.MTX), ncol(curr.MTX))
		attr(curr.MTX, 'dimnames') <- list(
			seq_len(nrow(curr.MTX)),
			attr(curr.MTX, 'modelNames')
		)
		class(curr.MTX) <- 'matrix'
		curr.DF <- curr.MTX %>% as.data.frame %>% 
			mutate(G=attr(curr.MTX, 'G')) %>% 
			gather(Model,BIC,-G)
		curr.DF$BIC=curr.DF$BIC*-1
		return(
			mutate(
				curr.DF,
				Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE),
				best_G=curr.DF[which.min(curr.DF$BIC),'G'][[1]],
				best_stat=min(curr.DF$BIC,na.rm=TRUE),
				asterisk_col=c('black', rep(NA_character_, length(Species)-1))
			)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_line(aes(y=BIC, x=G, color=Model, linetype=Model)) +
		geom_point(aes(y=best_stat, x=best_G), size=4, shape=8) +
		theme_classic() +
		scale_y_reverse()+
		theme(
			strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', face='italic', size=3)
		) +
		xlab('Number of populations') +
		ylab('BIC') +
		scale_linetype_manual(values=rep(c('solid','dashed'),each=7)) +
		scale_color_manual(values=rep(gg_color_hue(7),2)) +
		facet_wrap(~ Species, ncol=4, scales='free_y')
})
```

@@

calc.fig.height <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	return(((n.plots %/% 5)+1) * 3)
}

valid.species <- function(i) {
	return((i <= n_distinct(spp.samples.DF$species)) & (!unique(spp.samples.DF$species)[i] %in% missing.species))
}
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (valid.species(1)) plot.spp.nmds(1)
 ```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (valid.species(3)) plot.spp.nmds(2)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (valid.species(3)) plot.spp.nmds(3)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (valid.species(4)) plot.spp.nmds(4)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (valid.species(5)) plot.spp.nmds(5)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (valid.species(6)) plot.spp.nmds(6)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (valid.species(7)) plot.spp.nmds(7)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (valid.species(8)) plot.spp.nmds(8)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (valid.species(9)) plot.spp.nmds(9)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (valid.species(10)) plot.spp.nmds(10)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (valid.species(11)) plot.spp.nmds(11)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (valid.species(12)) plot.spp.nmds(12)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (valid.species(13)) plot.spp.nmds(13)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (valid.species(14)) plot.spp.nmds(14)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (valid.species(15)) plot.spp.nmds(15)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (valid.species(16)) plot.spp.nmds(16)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (valid.species(17)) plot.spp.nmds(17)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (valid.species(18)) plot.spp.nmds(18)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (valid.species(19)) plot.spp.nmds(19)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (valid.species(20)) plot.spp.nmds(20)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (valid.species(21)) plot.spp.nmds(21)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (valid.species(22)) plot.spp.nmds(22)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (valid.species(23)) plot.spp.nmds(23)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (valid.species(24)) plot.spp.nmds(24)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (valid.species(25)) plot.spp.nmds(25)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (valid.species(26)) plot.spp.nmds(26)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (valid.species(27)) plot.spp.nmds(27)
```

>>>>

# define ggplot2 color wheel function
gg_color_hue <- function(n) {
	hues <- seq(15, 375, length=n+1)
	hcl(h=hues, l=65, c=100)[1:n]
}
```

```{r, echo=FALSE, fig.width=9.5, fig.height=10, out.width='7.5in', out.height='8.5in', fig.cap=paste0('Species distributions. Squares represent planning units. For a given species, planning units that were found to be inhabited are denoted with bright blue. Note that \\textit{',gsub('\\_', '\\ ', missing.species),'} was omitted from analysis.')}
## plot map of species distributions
# fortify data
spp.grid.FPLY <- ldply(unique(spp.samples.DF$species), function(x) {
		z <- grid.FPLY[,c('long', 'lat', 'group', x),drop=FALSE]
		names(z)[4] <- 'presence'
		z$species <- gsub('\\_', ' ', x)
		return(z)
	}
)
# plot species data
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spp.grid.FPLY, aes(x=long, y=lat, 
		group=group, fill=presence), alpha=0.8, color='grey10') +
	theme_classic() +
	guides(fill=guide_legend(title='Presence')) +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"),
		strip.background = element_rect(fill='grey20'),
		strip.text = element_text(color='white', face='italic'),
		axis.title=element_blank()
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	) +
	facet_wrap(~ species, ncol=4)
```

```{r, echo=FALSE, fig.width=4, fig.height=2.5, fig.cap="Species richness. Squares denote planning units. Planning units with a brighter color are inhabited by more species."}
# calculate species richness
grid.PLY$Species_richness <- grid.PLY@data %>%
	select(5:(4+n_distinct(spp.samples.DF$species))) %>% as.matrix() %>% rowSums()
# plot species richness
ggplot() +
	geom_polygon(data=countries.FPLY, aes(x=long, y=lat, group=group),
		fill='grey85', color='grey70') +
	geom_polygon(data=spFortify(grid.PLY), aes(x=long, y=lat, 
		group=group, fill=Species_richness), color='grey10') +
	scale_fill_gradientn(name='Richness (#)',
		colors=brewer.pal(9,'PuBu'),
		guide=guide_colorbar(ticks=element_line(color='black'), border=element_line(color='black'))
	) +
	theme_classic() +
	theme(
		axis.ticks=element_blank(), axis.text=element_blank(), axis.line=element_blank(), plot.margin = unit(c(0, 0, 0, 0), "lines"), axis.title=element_blank(),
		panel.border=element_rect(color='black', fill=NA, size=1)
	) +
	coord_cartesian(
		xlim=buffered.range(grid.FPLY$long, 0),
		ylim=buffered.range(grid.FPLY$lat, 0)
	)
```

@@

```{r, echo=FALSE, warning=FALSE, message=FALSE, fig.width=9.5, fig.height=10, fig.cap='Relative support ($BIC$) for the number of populations in each species. Each panel denotes a different species. Each line denotes a different model parametrization. Asterisks indicate the model and number of populations with the most support.'}
# format data
bic.DF <- ldply(
	seq_along(unique(spp.samples.DF$species)),
	.fun=function(i) {
		curr.MTX <- spp.Mclust.LST[[i]]$mclust$BIC
		attr(curr.MTX, 'dim') <- c(nrow(curr.MTX), ncol(curr.MTX))
		attr(curr.MTX, 'dimnames') <- list(
			seq_len(nrow(curr.MTX)),
			attr(curr.MTX, 'modelNames')
		)
		class(curr.MTX) <- 'matrix'
		curr.DF <- curr.MTX %>% as.data.frame %>% 
			mutate(G=attr(curr.MTX, 'G')) %>% 
			gather(Model,BIC,-G)
		curr.DF$BIC=curr.DF$BIC*-1
		return(
			mutate(
				curr.DF,
				Species=gsub('_', ' ', unique(spp.samples.DF$species)[i], fixed=TRUE),
				best_G=curr.DF[which.min(curr.DF$BIC),'G'][[1]],
				best_stat=min(curr.DF$BIC,na.rm=TRUE),
				asterisk_col=c('black', rep(NA_character_, length(Species)-1))
			)
		)
	}
)
# make plot
suppressWarnings({
	ggplot(data=bic.DF) +
		geom_line(aes(y=BIC, x=G, color=Model, linetype=Model)) +
		geom_point(aes(y=best_stat, x=best_G), size=4, shape=8) +
		theme_classic() +
		scale_y_reverse()+
		theme(
			strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white', face='italic', size=1)
		) +
		xlab('Number of populations') +
		ylab('BIC') +
		scale_linetype_manual(values=rep(c('solid','dashed'),each=7)) +
		scale_color_manual(values=rep(gg_color_hue(7),2)) +
		facet_wrap(~ Species, ncol=4, scales='free_y')
})
```

@@

calc.fig.height <- function(i) {
	# init
	adapt.col <- paste0(unique(spp.samples.DF$species)[i], '_adaptive_d1')
	neutral.col <- paste0(unique(spp.samples.DF$species)[i], '_neutral_d1')
	n.plots <- 0 
	# count adaptive plot
	if (adapt.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['adaptive']]$ndim
	# count neutral plot
	if (neutral.col %in% names(grid.FPLY))
		n.plots <- n.plots + spp.nmds.LST[[i]][['neutral']]$ndim
	# exports
	return(((n.plots %/% 5)+1) * 3)
}
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(1), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[1]),'}. Each panel shows a different dimension of the variation as indicated by its title. Squares represent planning units. The color of each planning unit panel corresponds to the average ordinated values associated with individuals sampled inside it. No indiviudals of this species were found inside the gray planning units.')}
if (1 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[1] %in% missing.species)) plot.spp.nmds(1)
 ```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(2), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[2]),'}. See Figure S6 caption for conventions.')}
if (2 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[2] %in% missing.species)) plot.spp.nmds(2)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(3), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[3]),'}. See Figure S6 caption for conventions.')}
if (3 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[3] %in% missing.species)) plot.spp.nmds(3)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(4), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[4]),'}. See Figure S6 caption for conventions.')}
if (4 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[4] %in% missing.species)) plot.spp.nmds(4)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(5), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[5]),'}. See Figure S6 caption for conventions.')}
if (5 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[5] %in% missing.species)) plot.spp.nmds(5)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(6), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[6]),'}. See Figure S6 caption for conventions.')}
if (6 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[6] %in% missing.species)) plot.spp.nmds(6)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(7), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[7]),'}. See Figure S6 caption for conventions.')}
if (7 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[7] %in% missing.species)) plot.spp.nmds(7)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(8), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[8]),'}. See Figure S6 caption for conventions.')}
if (8 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[8] %in% missing.species)) plot.spp.nmds(8)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(9), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[9]),'}. See Figure S6 caption for conventions.')}
if (9 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[9] %in% missing.species)) plot.spp.nmds(9)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(10), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[10]),'}. See Figure S6 caption for conventions.')}
if (10 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[10] %in% missing.species)) plot.spp.nmds(10)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(11), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[11]),'}. See Figure S6 caption for conventions.')}
if (11 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[11] %in% missing.species)) plot.spp.nmds(11)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(12), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[12]),'}. See Figure S6 caption for conventions.')}
if (12 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[12] %in% missing.species)) plot.spp.nmds(12)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(13), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[13]),'}. See Figure S6 caption for conventions.')}
if (13 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[13] %in% missing.species)) plot.spp.nmds(13)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(14), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[14]),'}. See Figure S6 caption for conventions.')}
if (14 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[14] %in% missing.species)) plot.spp.nmds(14)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(15), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[15]),'}. See Figure S6 caption for conventions.')}
if (15 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[15] %in% missing.species)) plot.spp.nmds(15)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(16), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[16]),'}. See Figure S6 caption for conventions.')}
if (16 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[16] %in% missing.species)) plot.spp.nmds(16)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(17), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[17]),'}. See Figure S6 caption for conventions.')}
if (17 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[17] %in% missing.species)) plot.spp.nmds(17)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(18), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[18]),'}. See Figure S6 caption for conventions.')}
if (18 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[18] %in% missing.species)) plot.spp.nmds(18)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(19), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[19]),'}. See Figure S6 caption for conventions.')}
if (19 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[19] %in% missing.species)) plot.spp.nmds(19)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(20), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[20]),'}. See Figure S6 caption for conventions.')}
if (20 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[20] %in% missing.species)) plot.spp.nmds(20)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(21), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[21]),'}. See Figure S6 caption for conventions.')}
if (21 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[21] %in% missing.species)) plot.spp.nmds(21)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(22), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[22]),'}. See Figure S6 caption for conventions.')}
if (22 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[22] %in% missing.species)) plot.spp.nmds(22)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(23), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[23]),'}. See Figure S6 caption for conventions.')}
if (23 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[23] %in% missing.species)) plot.spp.nmds(23)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(24), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[24]),'}. See Figure S6 caption for conventions.')}
if (24 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[24] %in% missing.species)) plot.spp.nmds(24)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(25), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[25]),'}. See Figure S6 caption for conventions.')}
if (25 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[25] %in% missing.species)) plot.spp.nmds(25)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(26), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[26]),'}. See Figure S6 caption for conventions.')}
if (26 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[26] %in% missing.species)) plot.spp.nmds(26)
```

```{r, echo=FALSE, fig.width=15, fig.height=calc.fig.height(27), fig.cap=paste0('Distribution of adaptive and neutral genetic variation in \\textit{',gsub('\\_', ' ', unique(spp.samples.DF$species)[27]),'}. See Figure S6 caption for conventions.')}
if (27 <= general.params.LST[[MODE]]$n.spp & (!unique(spp.samples.DF$species)[27] %in% missing.species)) plot.spp.nmds(27)
```
